Inverse energy transfer in three-dimensional quantum vortex flows

### 2025-10-06 main_REV.tex
Updated figures with new corrected colour scheme and hopf link data

The evolution of the vortex reconnection of a single pair is reported in Fig.~\ref{fig:visualisation}. 
The first row shows the reconnecting superfluid vortices (in green) accompanied by normal fluid structures generated by mutual friction, here displayed as enstrophy rendering $\bom(\x)^2=|\nabla\times \v_n|^2$. Such structures are the signature of the violent irreversible energy transfers in vortex reconnections 
\cite{stasiak2025experimental}. The second row shows the rendering of the local helicity $H(\x)=\v_n\cdot\bom$, where we observe a clear local helicity production, with an abrupt change of sign due to the rearrangement of the vortex topology. Remarkably, during reconnection there is a net 
sudden normal fluid helicity production, as shown in Fig.~\ref{fig:total-helicity}. We will come back to this finding later.
\begin{figure}[t]
    \centering
    \includegraphics*[width=0.48\textwidth]{helicity_total.pdf}
\caption{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$. For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$. $\tau_R = L_R/E^{1/2}_R$.
%\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the two reconnections occurring at different times; same colour scheme as in Fig.~\ref{fig:visualisation}.}
}
\label{fig:total-helicity}
\end{figure}

We now focus on the time evolution of the normal fluid energy spectrum $E(k)$, defined by 
\begin{equation}
    E = \frac{1}{(2\pi)^3}\int_{\mathcal{V}}\frac{1}{2}|\v_n|^2 dV = \int_0^{\infty}E(k)dk
\end{equation}
where $E$ is the total normal fluid energy and $k$ is the magnitude of the three-dimensional wavenumber. The energy at reconnection $E_R$ is given by $E(t_R)$, where $t_R$ is the time at reconnection. The energy spectrum $E(k)$ is displayed in Fig.~3a.
\begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]{energy-flux-spec.pdf}

    % \begin{subfigure}{0.49\textwidth}
    %     \centering
    %     \includegraphics*[width=\textwidth]{energy-spec.pdf}
    %     \caption{}\label{fig:kinetic-energy}
    % \end{subfigure}
    % \begin{subfigure}{0.49\textwidth}
    %     \centering
    %     \includegraphics*[width=\textwidth]{flux-spec.pdf}
    %     \caption{}\label{fig:energy-flux}
    % \end{subfigure}
% \begin{subcaptiongroup*}
% 	\phantomsubcaption\label{fig:minimum-distance}
% 	\phantomsubcaption\label{fig:prefactors}
% \end{subcaptiongroup*}

>>>>

The evolution of the vortex reconnection of a single pair is reported in Fig.~\ref{fig:visualisation}. 
The first row shows the reconnecting superfluid vortices (in green) accompanied by normal fluid structures generated by mutual friction, here displayed as enstrophy rendering $\bom(\x)^2=|\nabla\times \v_n|^2$. Such structures are the signature of the violent irreversible energy transfers in vortex reconnections 
\cite{stasiak2025experimental}. The second row shows the rendering of the local helicity $H(\x)=\v_n\cdot\bom$, where we observe a clear local helicity production, with an abrupt change of sign due to the rearrangement of the vortex topology. Remarkably, during reconnection there is a net 
sudden normal fluid helicity production, as shown in Fig.~\ref{fig:total-helicity}. We will come back to this finding later.
\begin{figure}[t]
    \centering

      \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{helicity_total.pdf}
        \caption{}\label{fig:}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{integral-scale-scaled.pdf}
        \caption{}\label{fig:}

    \end{subfigure}
\caption{\blue{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$. For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.}
%\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the two reconnections occurring at different times; same colour scheme as in Fig.~\ref{fig:visualisation}.}
}
\label{fig:total-helicity}
\end{figure}

We now focus on the time evolution of the normal fluid energy spectrum $E(k)$, defined by 
\begin{equation}
    E = \frac{1}{(2\pi)^3}\int_{\mathcal{V}}\frac{1}{2}|\v_n|^2 dV = \int_0^{\infty}E(k)dk
\end{equation}
where $E$ is the total normal fluid energy and $k$ is the magnitude of the three-dimensional wavenumber. The energy at reconnection $E_R$ is given by $E(t_R)$, where $t_R$ is the time at reconnection. The energy spectrum $E(k)$ is displayed in Fig.~3a.
\begin{figure}
    \centering
    % \includegraphics[width=0.49\textwidth]{energy-flux-spec.pdf}

    \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{energy-spec-scaled.pdf}
        \caption{}\label{fig:kinetic-energy}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{flux-spec-scaled.pdf}
        \caption{}\label{fig:energy-flux}
    \end{subfigure}
% \begin{subcaptiongroup*}
% 	\phantomsubcaption\label{fig:minimum-distance}
% 	\phantomsubcaption\label{fig:prefactors}
% \end{subcaptiongroup*}
